I\textsuperscript{2}CNER Project Report \\ Dynamic Transition Analysis With TIMES

### 2018-11-05 doc/2018-09-report/2018-09-i2cner-report.tex
report-minor corrections
Former-commit-id: e29eb807696e9071cbfd10da298df421261d7ae2 [formerly fb9e0afab2b52caeef72bf4ec58783f467bbad54]
Former-commit-id: a9c07d8dfcd4ea5b524b13361e1fa2dc0659f9ba

    %------------------------------------------------
    %    Report Number
    %------------------------------------------------
    \vspace{1cm}
    \textsc{\LARGE\bfseries UIUC-ARFC-2018-01} % Replace YYYY with the year, NN with report index
    \vspace{0.5cm}

@@

\item \textbf{Incorporation of nuclear, hydropower and renewables into the model} (June – August 2018): The process of incorporating these into the model was similar to the previous energy sources, but simpler, since the data obtained for these energy sources from EDMC was consistent across EDMC data tables and secondary sources \cite{noauthor_energy_2018} \cite{noauthor_iea_2017} \cite{noauthor_japan_2017}. We have also included processes for the projected growth of nuclear, solar and wind based on data from various studies, reports and articles. \cite{publicover_japan_2017} \cite{publicover_japan_2017} \cite{dincer_analysis_2011} \cite{noauthor_geothermal_2018} \cite{heger_wind_2016} \cite{noauthor_operational_2013} \cite{noauthor_electricity_2017}

>>>>

    %------------------------------------------------
    %    Report Number
    %------------------------------------------------
    \vspace{1cm}
    \textsc{\LARGE\bfseries UIUC-ARFC-2018-00} \textit{work in progress} % Replace YYYY with the year, NN with report index
    \vspace{0.5cm}

@@

\item \textbf{Incorporation of nuclear, hydropower and renewables into the model} (June – August 2018): The process of incorporating these into the model was similar to the previous energy sources, but simpler, since the data obtained for these energy sources from EDMC was consistent across EDMC data tables and secondary sources \cite{noauthor_energy_2018} \cite{noauthor_iea_2017} \cite{noauthor_japan_2017}. We have also included processes for the projected growth of nuclear, solar and wind based on data from various studies, reports and articles. \cite{publicover_japan_2017} \cite{dincer_analysis_2011} \cite{noauthor_geothermal_2018} \cite{heger_wind_2016} \cite{noauthor_operational_2013} \cite{noauthor_electricity_2017}
